Treatment effects

### 2017-06-28 Paper/main.tex
replace png to tiff

\begin{figure}[H]
    \caption{Belief updating after treatment}
    \label{Figure_updating}
    \begin{center}
%    \begin{subfigure}{\textwidth}
%        \caption{update in beliefs in duration}
%        \centering
%        \includegraphics[width=\textwidth]{updatebeleif_duration.pdf}
%    \end{subfigure}
    \begin{subfigure}{\textwidth}
        \caption{Update in beliefs in amount}
        \centering
        \includegraphics[width=\textwidth]{updatebeleif_amount.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: Graphs on belief updating. They show the difference (exit-baseline) in amount (in tens-of-thousand pesos) between what's reported in exit and baseline surveys. In order to drop outliers in our sample, we did some trimming and kept survey observations with $\mid exit - baseline \mid < 50k$. This implied dropping 17 obs. for employee surveys, 67 for employee lawyer and 68 for firm lawyer surveys.} 
      \footnotesize{ \textit{Do file: }  \texttt{Update\_beleifs.do}}
\end{figure}

@@

\begin{figure}[H]
    \caption{ }
    \label{}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=1\textwidth]{}
     \end{subfigure}

        \begin{subfigure}{0.49\textwidth}    
         \centering
        \includegraphics[width=1\textwidth]{}
     \end{subfigure}

     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=1\textwidth]{}
     \end{subfigure}

>>>>

\begin{figure}[H]
    \caption{Belief updating after treatment}
    \label{Figure_updating}
    \begin{center}
%    \begin{subfigure}{\textwidth}
%        \caption{update in beliefs in duration}
%        \centering
%        \includegraphics[width=\textwidth]{updatebeleif_duration.pdf}
%    \end{subfigure}
    \begin{subfigure}{\textwidth}
        \caption{Update in beliefs in amount}
        \centering
        \includegraphics[width=\textwidth]{updatebeleif_amount.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: Graphs on belief updating. They show the following statistic: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won. Note that when $\theta=1$ we have no update with respect to the prediction. And when $\theta<1$ they update in the direction of what calculator says. The extreme case $\theta=0$ implies perfect updating with respect to what the calculator says.} 
      \footnotesize{ \textit{Do file: }  \texttt{Update\_beleifs.do}}
\end{figure}

@@

\begin{figure}[H]
    \caption{ }
    \label{}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=1\textwidth]{oos_fit_liqtotal.tiff}
     \end{subfigure}

        \begin{subfigure}{0.49\textwidth}    
         \centering
        \includegraphics[width=1\textwidth]{oos_fit_duracion.tiff}
     \end{subfigure}

     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=1\textwidth]{oss_fit_categorical.tiff}
     \end{subfigure}

### 2017-06-28 ScaleUp/ITT_ATT.tex
Changes in SS Tables and in Figures amountasked and con_overtime
Updated paper
replace png to tiff

@@

>>>>

\begin{landscape}
\begin{center}
\scriptsize{\input{\folder/ITT_ATT_report.tex}}
\end{center}

@@

\begin{figure}[H]
\label{update}
\begin{center}
\includegraphics[width=\textwidth]{./Figures/updatebeleif_amount.pdf}
\end{center}
{\footnotesize \textit{Notes: Graphs on belief updating. They show the following statistic: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won. Note that when $\theta=1$ we have no update with respect to the prediction. And when $\theta<1$ they update in the direction of what calculator says. The extreme case $\theta=0$ implies perfect updating with respect to what the calculator says. }}
{\footnotesize \textit{Do file: } \texttt{Update\_beleifs.do}}
\end{figure}

The following table displays a regression of conciliation against the statistics of updating
\[\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|\]

\begin{center}
\scriptsize{\input{\folder/con_vs_update.tex}}
\end{center}
